Research Notes

### 2018-03-05 writups/notes.tex
regenerate png, add some notes

@@

Sourced from \url{https://people.maths.ox.ac.uk/trefethen/6all.pdf}. There are
largely two ways to do this. The first is to add a damping zone, a region in
which $\dot{q} = -q/\tau_d(z)$ where $\tau_d(0) = 0$ and increases to some
non-small number for some $z_0$ beyond which we want damping.

>>>>

\subsection{Extracting Information from the Waveform}

Let's make sure we can extract information from the linearized problem. Notable
things we should be interested in: phase/group velocity, energy density and
energy flux.

Let's first consider the phase velocity. We traditionally think about the phase
velocity in 1D $v_{ph} = \frac{\omega(k)}{k}$, but in general it is the function
such that $\vec{k} \cdot \vec{r} - \omega t = \vec{k} \cdot \p*{\vec{r} -
\vec{v}_{ph}t}$ is constant (the phase of the wave). Thus, it must satisfy
$\vec{k} \cdot \vec{v}_{ph} = \omega$, and so one sensible choice is
$\vec{v}_{ph} = \frac{\omega \hat{k}}{\abs{\vec{k}}} = \frac{\omega
\vec{k}}{\abs{\vec{k}}^2}$. Thus, if we have some waveform $f(x, z, t)$, we can
estimate its phase velocity $\vec{v}_{ph}(x, z, t)$ by
\begin{equation}
    \vec{v}_{ph}(x, z, t) = \frac{\partial_t f
        \vec{\nabla}f}{\abs{\vec{\nabla}f}^2}.\label{eq:v_ph}
\end{equation}
This can be validated in the $f(x, z, t) \propto e^{i(\vec{k} \cdot \vec{x} -
\omega t)}$ case to give $\vec{v}_{ph} = \frac{\omega \vec{k}}{k^2}$. Note the
sign in \autoref{eq:v_ph}

@@

Sourced from \url{https://people.maths.ox.ac.uk/trefethen/6all.pdf}. There are
largely two ways to do this. The first is to add a damping zone, a region in
which $\dot{q} = -q/\tau_d(z)$ where $\tau_d(0) = 0$ and increases to some
non-small number for some $z_0$ beyond which we want damping. One form, chosen
in Ryan and Dong's paper, is to use multiplicative factor $f(z) = \max\s*{0, 1 -
\frac{\p*{z - z_b}^2}{\p*{z_d - z_b}^2}}$ where $z_b$ is where one begins
supression and $z_b$ is the boundary. Then a dynamical variable $q$ can be
supressed via $\dot{q} = (\dots) - f(z)\frac{q - q_0}{\tau}$ where $\tau$ is the
dynamical timescale on which to damp and $q_0$ is the value to damp to.
